Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-10-04 paper/main.tex
update paper

Using the CasJobs server, we randomly select a total of 65,000 sources,
which are either stars or galaxies.
\changed{
In this work, we exclude objects that clearly are neither stars nor galaxies.
Most of the excluded objects are QSOs or quasars.
Quasars appear as point sources, rather than resolved sources similar to
galaxies,
and many of them have one or more saturated pixels in the images.
However, unlike any known stars, their spectra show strong and broad emission
lines.
Quasars are also different from galaxies because of their intrinsic variability
on a wide range of time scales, which may be due to variation in the accretion
rate or instabilities of the accretion disk around the black hole
\citep{popovic2012photocentric}.
Thus, many studies exclude quasars in the binary star-galaxy classification
scheme~\citep[\eg][]{vasconcellos2011decision,Fadely2012}.
Expanding the historical star-galaxy classification problem to include
additional classes, \eg \textit{nsng} (neither star nor galaxy),
may have advantanges~\citep{ball2006robust}, and we plan to present
the results of this multi-class problem in a future paper.
}

>>>>

Using the CasJobs server, we randomly select a total of 65,000 sources,
which are either stars or galaxies.
\changed{
In this work, we exclude objects that clearly are neither stars nor galaxies.
Most of the excluded objects are QSOs or quasars.
Quasars appear as point sources, rather than resolved sources similar to
galaxies,
and many of them have one or more saturated pixels in the images.
However, unlike any known stars, their spectra show strong and broad emission
lines.
Quasars are also different from galaxies because of their intrinsic variability
on a wide range of time scales, which may be due to variation in the accretion
rate or instabilities of the accretion disk around the black hole
\citep{popovic2012photocentric}.
Thus, many studies exclude quasars in the binary star-galaxy classification
scheme~\citep[\eg][]{vasconcellos2011decision,Fadely2012}.
Expanding the historical star-galaxy classification problem to include
additional classes, \eg \textit{nsng} (neither star nor galaxy),
may have advantages~\citep{ball2006robust}, and we plan to present
the results of this multi-class problem in a future paper.
}
